---
title: "Graph Challenge 2"
author: "Your Name Here"
date: "`r Sys.Date()`"
format: 
  docx:
    reference-doc: ../quarto_template.docx
    number-sections: true
    number-depth: 3
    fig-dpi: 500
    fig-align: center
    fig-height: 4
    fig-width: 6
execute: 
  echo: true
  warning: false
  message: false
---

You can use data to tell many different, sometimes conflicting, stories. Below we have some code written by an analyst who claims there was fraud in the 2012 US Presidential Election between then Democratic incumbent Barack Obama and his Republican challenger Mitt Romney. After reading in the data, this analyst made two data visualizations that he believes show something is amiss about the election. The data records for all counties in the lower 48 US states vote totals and county population in the 2008 and 2012 US Presidential Elections. With this data, the analyst made a bar plot that summarizes the sum total of counties where Obama and Romney won the popular vote. He then made a scatter plot with a smoothed linear regression line of best fit showing the sum of ballots cast for Romney across counties by county population. If you run the code, you'll see that Romney won a strong majority of counties, and that larger counties cast more ballots for Romney than smaller counties did. *How can it be that Obama won in 2012?!*

For this graph challenge, you mission is to update the below figures in ways that help our misguided analyst see that he's missed some important details about the 2012 election. (Hint: Try faceting by the variable `pop_decile` for the first data viz.) When you're done, render your work and submit to Canvas.

```{r}
## Open the packages you need
library(tidyverse)

## Attach the data
read_csv(
  here::here("_data", "election.csv")
) -> dt

```



```{r}
## Here's the first plot the analyst made:
dt |>
  drop_na() |>
  ggplot() +
  aes(x = winner12, fill = winner12) +
  geom_bar() +
  scale_x_discrete(
    breaks = NULL
  ) +
  scale_y_continuous(
    labels = scales::comma
  ) +
  labs(
    title = paste0(
      "Romney won a strong majority of counties\n",
      "in 2012"
    ),
    subtitle = "Sum of counties won by each candidate:",
    x = NULL,
    y = NULL,
    fill = "Counties won by..."
  )
```


```{r}
## Your updated plot should go here:

```


```{r}
## Here's the second plot the analyst made:
ggplot(dt) +
  aes(x = pop, y = rep2012) +
  geom_point(
    color = "gray"
  ) +
  geom_smooth(
    method = "lm",
    se = F,
    color = "steelblue"
  ) +
  scale_x_log10(
    labels = scales::comma
  ) +
  scale_y_log10(
    labels = scales::comma
  ) +
  labs(
    x = "County Population",
    y = "Ballots Cast for Romney",
    title = paste0(
      "Larger counties cast more votes for Romney\n",
      "than smaller counties"
    )
  )
```


```{r}
## Your updated second plot should go here:

```

